Perceptions and Preferences for Meritocracy in Survey Research

### 2023-05-18 paper.Rmd
ajustes template.tex

---
title: "Perceptions and Preferences for Meritocracy in Survey Research"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
params:
  lang: en
author: 
- name: Juan Carlos Castillo
  affiliation: Department of Sociology, Universidad de Chile
  email: juancastillov@uchile.cl
  number: 1
- name: Julio Iturra
  affiliation: Bremen International Graduate School of Social Sciences, Universität Bremen
  number: 2
- name: Luis Maldonado
  affiliation: Institute of Sociology, Universidad Católica de Chile
  number: 3
- name: Francisco Meneses
  affiliation: 
  number: 1
- name: Jorge Atria
  affiliation: Department of Sociology, Universidad Diego Portales, Chile
  number: 5
abstract: |
  Economic and social inequalities are causing growing concerns and crises in contemporary societies. One factor suggested to explain the persistence of inequality is the belief in meritocracy, which justifies economic disparities based on differences in effort and talent. However, empirical research on meritocracy is relatively new and characterized by diverse conceptualizations and measures, leading to inconsistent findings and interpretations. To address this issue, the present paper proposes a conceptual and measurement framework for perceptions and preferences regarding meritocracy and non-meritocracy, focusing on comparative survey research methodologies. The proposal is first tested through confirmatory factor analysis (CFA) using data from the International Social Survey Programme (ISSP) inequality module, commonly used in comparative research on meritocracy. Based on these findings,  a second study focuses on developing a novel scale that better captures the distinction between perceptions and preferences related to meritocracy. This scale is tested using a sample of 2,141 individuals from Chile. The results of this study contribute to refining the measurement of meritocracy and non-meritocracy and shed light on the importance of considering different dimensions when studying meritocracy in survey research, both conceptually and empirically.
  \newline
  \newline

   **Keywords**: meritocracy, survey methodology, social inequality, construct measurement 
output:
  bookdown::word_document2:
    number_sections: false
    reference_docx: input/template.docx
    toc: false
  bookdown::pdf_document2:
    template: null
    number_sections: false    
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion    
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - input/bib/meritocracy.bib
csl: input/bib/apa7-singlespace.csl
editor_options:
  chunk_output_type: console
geometry: margin=1in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \hypersetup {colorlinks = true, linkcolor = blue, urlcolor = blue}    
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[british,UKenglish,USenglish,american]{babel}
always_allow_html: true # for word output
fontsize: 10pt
papersize: a4
---

>>>>

---
title: "Perceptions and Preferences for Meritocracy in Survey Research"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
# params:
# lang: en-GB
author: 
- name: Juan Carlos Castillo
  affiliation: Department of Sociology, Universidad de Chile
  email: juancastillov@uchile.cl
  number: 1
- name: Julio Iturra
  affiliation: Bremen International Graduate School of Social Sciences, Universität Bremen
  number: 2
- name: Luis Maldonado
  affiliation: Institute of Sociology, Universidad Católica de Chile
  number: 3
- name: Francisco Meneses
  affiliation: 
  number: 1
- name: Jorge Atria
  affiliation: Department of Sociology, Universidad Diego Portales, Chile
  number: 5
abstract: |
  Economic and social inequalities are causing growing concerns and crises in contemporary societies. One factor suggested to explain the persistence of inequality is the belief in meritocracy, which justifies economic disparities based on differences in effort and talent. However, empirical research on meritocracy is relatively new and characterized by diverse conceptualizations and measures, leading to inconsistent findings and interpretations. To address this issue, the present paper proposes a conceptual and measurement framework for perceptions and preferences regarding meritocracy and non-meritocracy, focusing on comparative survey research methodologies. The proposal is first tested through confirmatory factor analysis (CFA) using data from the International Social Survey Programme (ISSP) inequality module, commonly used in comparative research on meritocracy. Based on these findings,  a second study focuses on developing a novel scale that better captures the distinction between perceptions and preferences related to meritocracy. This scale is tested using a sample of 2,141 individuals from Chile. The results of this study contribute to refining the measurement of meritocracy and non-meritocracy and shed light on the importance of considering different dimensions when studying meritocracy in survey research, both conceptually and empirically.
  \newline
  \newline

   **Keywords**: meritocracy, survey methodology, social inequality, construct measurement 
output:
  bookdown::word_document2:
    number_sections: false
    reference_docx: input/template.docx
    toc: false
  bookdown::pdf_document2:
    template: null
    number_sections: false    
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion    
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - input/bib/meritocracy.bib
csl: input/bib/apa7-singlespace.csl
editor_options:
  chunk_output_type: console
geometry: margin=1in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \hypersetup {colorlinks = true, linkcolor = blue, urlcolor = blue}    
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  # - \usepackage[british,UKenglish,USenglish,american]{babel}
always_allow_html: true # for word output
fontsize: 10pt
papersize: a4
---
